Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-21 paper.tex
a few minor tweaks

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Fresh fuel for LWRs is provided directly from enrichment with infinite supply and throughput. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2000 MTHM/yr capacity and increases to 3000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it becomes
available for separation: 5 years for cooling and an additional 2 years to approximate non-instantaneous separations and fabrication times. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.  Compositions used for the simulations
were simple containing primarily $^{238}U$, $^{235}U$, $^{239}Pu$, $^{241}Am$,
and small quantities of a few lanthanides.  Full composition details can be
found in the Cyclus input files used \cite{Carlsen2015}.

@@

\begin{equation}
    P_{outage}(t) = \sum\limits_{r \in R_t} C_r \cdot H[t-(\tau(t,r) + \Delta\;t_{out})] \cdot [1-O(t,r)]
    \label{eq:shortage}
\end{equation}

where $R_t$ is the set of all reactors, $C_r$ is the power capacity of reactor
$r$, $H$ is the Heaviside function, $\tau(t,r)$ is the beginning of the most
recent refueling outage of reactor $r$ before $t$, $\Delta\; t_{out}$ is the
normal refueling outage duration, and $O(t,r)$ is 1 if reactor $r$ is
producing power at time $t$ and zero otherwise.

>>>>

The scenario starts with 100 LWRs and follows an exponential curve with a 1\%
annual growth rate for 200 years.  The decommissioning of the initial 100
reactors is staggered over years 15 to 55.  Fresh fuel for LWRs is provided directly from enrichment with infinite supply and throughput. In year 35, fast reactors become available for
deployment and no more thermal reactors are built.  LWR spent fuel separations
begins in year 15 with 2000 MTHM/yr capacity and increases to 3000 MTHM/yr in
year 25.  Fast reactor spent fuel separations and fuel fabrication have
infinite capacity.  All spent fuel is stored/cooled for 7 years before it becomes
available for separation: 5 years for cooling and an additional 2 years to approximate non-instantaneous separations and fabrication times. Figure \ref{fig:flow} shows the material flow
relationships between the facilities.  Compositions used for the simulations
were simple containing $^{238}U$, $^{235}U$, $^{239}Pu$, $^{241}Am$,
and small quantities of a few lanthanides.  Full composition details can be
found in the Cyclus input files used \cite{Carlsen2015}.

@@

\begin{equation}
    P_{outage}(t) = \sum\limits_{r \in R_t} P_r \cdot H[t-(\tau(t,r) + \Delta\;t_{out})] \cdot [1-O(t,r)]
    \label{eq:shortage}
\end{equation}

where $R_t$ is the set of all reactors, $P_r$ is the power capacity of reactor
$r$, $H$ is the Heaviside function, $\tau(t,r)$ is the beginning of the most
recent refueling outage of reactor $r$ before $t$, $\Delta\; t_{out}$ is the
normal refueling outage duration, and $O(t,r)$ is 1 if reactor $r$ is
producing power at time $t$ and zero otherwise.
